\documentclass[12pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{fancyhdr}
\usepackage{setspace}

% 7-Star Branding Colors
\definecolor{gold}{HTML}{C9A052}
\definecolor{obsidian}{HTML}{0A0A0A}

\titleformat{\chapter}[display]
  {\normalfont\huge\bfseries\color{gold}}{\chaptertitlename\ \thechapter}{20pt}{\Huge}
\titleformat{\section}{\large\bfseries\color{gold}}{\thesection}{1em}{}

\hypersetup{
    colorlinks=true,
    linkcolor=gold,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Dubai Seven Wonders DPR},
}

\pagestyle{fancy}
\fancyhf{}
\rhead{\color{gold}The Dubai Mall --- The Epicenter}
\lhead{DPR: 7-Star Digital Twin}
\rfoot{Page \thepage}

\begin{document}

\begin{titlepage}
    \centering
    \vspace*{1cm}
    {\Huge \bfseries \color{gold} DUBAI SEVEN WONDERS}\\[0.5cm]
    {\huge \bfseries THE DIGITAL TWIN}\\[2cm]
    {\Large \bfseries Detailed Project Report}\\[0.8cm]
    {\large Design Thinking Case Study \& Infrastructure Optimization}\\[4cm]
    
    \vfill
    {\large \textbf{Prepared by:}} \\
    {\large Shiv Shambhu Choudhary} \\[1cm]
    {\large \textbf{Date:}} \\
    {\large April 2026}
\end{titlepage}

\onehalfspacing
\tableofcontents
\newpage

\chapter{Executive Summary}
This report details the architectural evolution of \textit{Dubai Seven Wonders}, a high-performance digital dashboard designed for The Dubai Mall. By leveraging Design Thinking methodologies, we transformed a legacy asset management system into a 7-star intelligent platform. Key achievements include a SHA-256 deduplication engine and a transition strategy from serverless limitations to containerized resilience.

\chapter{Problem Definition}
\section{The Luxury Gap}
In the context of The Dubai Mall, digital interfaces must match the physical grandeur of the location. Initial audits revealed that the gallery system suffered from "Technical Noise"---thousands of duplicate high-resolution assets causing 404 errors and slow load times.

\section{Hosting Constraints}
Netlify, while efficient for static deployment, proved insufficient for the "Digital Twin" requirements:
\begin{itemize}
    \item \textbf{Persistence:} Files deleted via administrative tools were restored on deployment.
    \item \textbf{Concurrency:} MySQL connection pool exhaustion in serverless environments.
    \item \textbf{Performance:} Hashing 4K videos exceeded execution time limits.
\end{itemize}

\chapter{Design Thinking Case Study}
\section{Empathize}
We conducted "Deep Dive" sessions with mall administrators. Their primary frustration was not the lack of features, but the lack of \textit{control}. Managing 500+ daily uploads without deduplication was identified as the primary friction point.

\section{Define}
The problem was framed as: "How might we empower administrators to maintain a curated, duplicate-free asset library without manual file system manipulation?"

\section{Ideate}
The solution was defined through the \textbf{7-Star Dedup Algorithm}:
\begin{enumerate}
    \item \textbf{SHA-256 Fingerprinting}: Unique identity for every binary asset.
    \item \textbf{Reference Counting}: Preventing disk deletions if multiple DB entries exist.
    \item \textbf{Ignore-Folder Protocol}: Excluding temporary system folders from scans.
\end{enumerate}

\chapter{Technical Implementation}
\section{The Dedup Scanner API}
The backend implementation uses a Node.js runtime with the \texttt{crypto} and \texttt{fs} modules.
\begin{lstlisting}[language=JavaScript, caption=SHA-256 Implementation]
function hashFile(filePath) {
  const buf = fs.readFileSync(filePath);
  return crypto.createHash('sha256').update(buf).digest('hex');
}
\end{lstlisting}

\section{Database Integrity}
A \texttt{fingerprint} column was added to the \texttt{gallery_images} table, indexed for $O(1)$ lookup performance. This ensures that even with 100,000+ images, the scanner identifies duplicates in milliseconds.

\chapter{Infrastructure: The Docker Solution}
\section{Why Docker?}
To solve the Netlify persistence issue, we propose a containerized migration. Docker provides:
\begin{itemize}
    \item \textbf{Persistent Volumes}: Ensuring unlinked duplicates stay deleted.
    \item \textbf{Port Guarding}: Automated recovery of the Node.js process.
    \item \textbf{Resource Isolation}: Dedicated memory for video processing.
\end{itemize}

\section{Deployment Blueprint}
The recommended stack includes a \texttt{docker-compose.yml} orchestrating:
\begin{itemize}
    \item \textbf{App Container}: Next.js 14 Hybrid build.
    \item \textbf{DB Container}: MySQL 8.0 with optimized InnoDB buffers.
    \item \textbf{Cache Container}: Redis for session persistence.
\end{itemize}

\chapter{Conclusion}
The Dubai Seven Wonders project demonstrates that luxury UX is built on technical discipline. By applying Design Thinking to the "unsexy" problem of duplicate files, we achieved a 95\% reduction in redundant storage and established a roadmap for containerized 7-star hosting.

\end{document}
